### 2016-10-31 thesis/intro/intro.tex
tmp commit

\noindent
The first key factor that contirbutes to the global rise in obese population is the availability and abundance of certain food in the country.
With the help from government trade policies, food and other goods have become easier to trade between the country, helping the economic growth of many countries around the world (citation -- Kearney?).
This led to greater abundance of food in general, greater number of choices of food and shifted the overall nutritional status of the country \citep{Malik2013}.
This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in a different, much larger problem -- obesity.

As an example, in the \gls{usa}, the cost of corn and soy is low due to the fact that they are the raw ingredients for most processed food and beverages, such as high fructose corn syrups used to sweeten many soft drinks in the \gls{usa} \citep{Malik2013}.
Moreover, corn and soy are also the main food for the livestock, which results in lower prices for meat \citep{Malik2013}.
On the othere hand, the prices of fruits and vegetables remain expensive due to the lack of support by the government to lower the cost associated with the production (more citation...) \citep{Malik2013}.

@@

It is unfair for urbanisation to take all of the blame for the lack of exercise in the population, but it is true that urbanisation makes the bar higher for many people to take up the recommended level of exercise and maintain it.\\

@@

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet made by the population.
The amount of low-quality food have increased significantly in many rapidly growing countries, as these high-energy, low-nutritional food are cheaper and more profitible than the natural produce that have higher nutritional value (citation).
As a result, more people tend to purchase these low-quality food more often, and consume more energy than they are required.

Many people eat responsibly and avoid these low-quality diet and prevent overconsumption of such food.
However, the overconsumption of these food is not a big problem as such, but rather the overall quality of the food \citep{Malik2013}.
These food are usually high in refined sugar and unhealthy fat, highly processed, contain very little nutritional value and low in fibre.
Thus consuming these food, especially food that are high in saturated fats,

The abundance of food that are high in energy and low in nutritional value have increased significantly.
In contrast to this, the amount of  natural produces have decreased.

\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}

\citep{Malik2013}
\\

@@

As mentioned at the beginning of the current section, obesity has a devastating effect on the health of the population globally.

>>>>

\noindent
The first key factor that contirbutes to the global rise in obese population is the availability and abundance of certain food in the country.
With the help from government trade policies, food and other goods have become easier to trade between the country, helping the economic growth of many countries around the world \citep{Kearney2010}.
This led to greater abundance of food in general, greater number of choices of food and shifted the overall nutritional status of the country \citep{Malik2013}.
This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in a different, much larger problem -- obesity.

As an example, in the \gls{usa}, the cost of corn and soy is low due to the fact that they are the raw ingredients for most processed food and beverages, such as high fructose corn syrups used to sweeten many soft drinks in the \gls{usa} \citep{Malik2013}.
Moreover, corn and soy are also the main food for the livestock, which results in lower prices for meat \citep{Malik2013}.
On the othere hand, the prices of fruits and vegetables remain expensive due to the lack of support by the government to lower the cost associated with the production \citep{Malik2013}.

@@

Urbanisation by itself cannot be accounted for the lack of exercise in the population, but it is true that urbanisation makes the bar higher for many people to take up the recommended level of fitness and maintain it. \\

@@

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet made by the population.
The amount of low-quality food have increased significantly in many rapidly growing countries, as these high-energy, low-nutritional food are cheaper and more profitible than the natural produce that have higher nutritional value \citep{Kearney2010}.
As a result, more people tend to purchase these low-quality food more often, and consume more energy than they are required.

However, many people eat responsibly and avoid these low-quality diet and prevent overconsumption of such food, but the overconsumption of these food is not a big problem as such, rather the overall quality of the food \citep{Malik2013}.
These food are usually high in refined sugar and unhealthy fat, highly processed, contain very little nutritional value and are low in fibre.
As a result, consumption of these food increases the overall energy intake and achieve no nutritional benefits from the food.

Whether it is by choice or not, consumption of these low-quality diet leads to obesity and obesity-related diseases. \\

% All of these population-level, factors together with the individual-level factors, contribute to the obesity status of the population.

@@

As mentioned at the beginning of the current section, obesity has a devastating effect on the health of the population in a global scale.
